### 2025-07-23 paper/preprint/paper.tex
going with Alek's suggestions for standardization and baselines

\begin{tcolorbox}[enhanced jigsaw, opacityback=0, bottomtitle=1mm, arc=.35mm, colback=white, coltitle=black, bottomrule=.15mm, breakable, leftrule=.75mm, title={Note \ref*{nte-train-default}: Training Phase}, toprule=.15mm, colframe=quarto-callout-note-color-frame, toptitle=1mm, opacitybacktitle=0.6, left=2mm, titlerule=0mm, rightrule=.15mm, colbacktitle=quarto-callout-note-color!10!white]

@@

\begin{tcolorbox}[enhanced jigsaw, opacityback=0, bottomtitle=1mm, arc=.35mm, colback=white, coltitle=black, bottomrule=.15mm, breakable, leftrule=.75mm, title={Note \ref*{nte-eval-default}: Evaluation Phase}, toprule=.15mm, colframe=quarto-callout-note-color-frame, toptitle=1mm, opacitybacktitle=0.6, left=2mm, titlerule=0mm, rightrule=.15mm, colbacktitle=quarto-callout-note-color!10!white]

@@

@@

\begin{tabular}{lc}
  \toprule
  \textbf{Data} & \textbf{Cost $(-\%)$} \\\midrule
  LS & -26.82\pm0.86 $^{*}$ \\
  Circ & 40.97\pm0.82 $^{*}$ \\
  Moon & 33.83\pm0.98 $^{*}$ \\
  OL & 10.35\pm1.28 $^{*}$ \\\midrule
  Adult & 1.16\pm3.53 $^{}$ \\
  CH & -34.89\pm2.31 $^{*}$ \\
  Cred & 28.24\pm1.08 $^{*}$ \\
  GMSC & 3.54\pm5.78 $^{}$ \\
  MNIST & -31.67\pm7.72 $^{*}$ \\\midrule
  Avg. & 2.75 \\\bottomrule
\end{tabular}

@@

\begin{tcolorbox}[enhanced jigsaw, opacityback=0, bottomtitle=1mm, arc=.35mm, colback=white, coltitle=black, bottomrule=.15mm, breakable, leftrule=.75mm, title={Note \ref*{nte-gen-params-final-run-train}: Training Phase}, toprule=.15mm, colframe=quarto-callout-note-color-frame, toptitle=1mm, opacitybacktitle=0.6, left=2mm, titlerule=0mm, rightrule=.15mm, colbacktitle=quarto-callout-note-color!10!white]

@@

\begin{tcolorbox}[enhanced jigsaw, opacityback=0, bottomtitle=1mm, arc=.35mm, colback=white, coltitle=black, bottomrule=.15mm, breakable, leftrule=.75mm, title={Note \ref*{nte-gen-params-final-run-eval}: Evaluation Phase}, toprule=.15mm, colframe=quarto-callout-note-color-frame, toptitle=1mm, opacitybacktitle=0.6, left=2mm, titlerule=0mm, rightrule=.15mm, colbacktitle=quarto-callout-note-color!10!white]

@@

\begin{tcolorbox}[enhanced jigsaw, opacityback=0, bottomtitle=1mm, arc=.35mm, colback=white, coltitle=black, bottomrule=.15mm, breakable, leftrule=.75mm, title={Note \ref*{nte-pen-final-run-train}: Training Phase}, toprule=.15mm, colframe=quarto-callout-note-color-frame, toptitle=1mm, opacitybacktitle=0.6, left=2mm, titlerule=0mm, rightrule=.15mm, colbacktitle=quarto-callout-note-color!10!white]

@@

\begin{tcolorbox}[enhanced jigsaw, opacityback=0, bottomtitle=1mm, arc=.35mm, colback=white, coltitle=black, bottomrule=.15mm, breakable, leftrule=.75mm, title={Note \ref*{nte-pen-final-run-eval}: Evaluation Phase}, toprule=.15mm, colframe=quarto-callout-note-color-frame, toptitle=1mm, opacitybacktitle=0.6, left=2mm, titlerule=0mm, rightrule=.15mm, colbacktitle=quarto-callout-note-color!10!white]

@@

\begin{tcolorbox}[enhanced jigsaw, opacityback=0, bottomtitle=1mm, arc=.35mm, colback=white, coltitle=black, bottomrule=.15mm, breakable, leftrule=.75mm, title={Note \ref*{nte-train-final-run-train}: Training Phase}, toprule=.15mm, colframe=quarto-callout-note-color-frame, toptitle=1mm, opacitybacktitle=0.6, left=2mm, titlerule=0mm, rightrule=.15mm, colbacktitle=quarto-callout-note-color!10!white]

@@

\begin{tcolorbox}[enhanced jigsaw, opacityback=0, bottomtitle=1mm, arc=.35mm, colback=white, coltitle=black, bottomrule=.15mm, breakable, leftrule=.75mm, title={Note \ref*{nte-train-final-run-eval}: Evaluation Phase}, toprule=.15mm, colframe=quarto-callout-note-color-frame, toptitle=1mm, opacitybacktitle=0.6, left=2mm, titlerule=0mm, rightrule=.15mm, colbacktitle=quarto-callout-note-color!10!white]

@@

\begin{tcolorbox}[enhanced jigsaw, opacityback=0, bottomtitle=1mm, arc=.35mm, colback=white, coltitle=black, bottomrule=.15mm, breakable, leftrule=.75mm, title={Note \ref*{nte-tune-train}: Training Phase}, toprule=.15mm, colframe=quarto-callout-note-color-frame, toptitle=1mm, opacitybacktitle=0.6, left=2mm, titlerule=0mm, rightrule=.15mm, colbacktitle=quarto-callout-note-color!10!white]

@@

\begin{tcolorbox}[enhanced jigsaw, opacityback=0, bottomtitle=1mm, arc=.35mm, colback=white, coltitle=black, bottomrule=.15mm, breakable, leftrule=.75mm, title={Note \ref*{nte-tune-eval}: Evaluation Phase}, toprule=.15mm, colframe=quarto-callout-note-color-frame, toptitle=1mm, opacitybacktitle=0.6, left=2mm, titlerule=0mm, rightrule=.15mm, colbacktitle=quarto-callout-note-color!10!white]

@@

\begin{tcolorbox}[enhanced jigsaw, opacityback=0, bottomtitle=1mm, arc=.35mm, colback=white, coltitle=black, bottomrule=.15mm, breakable, leftrule=.75mm, title={Note \ref*{nte-tune_lr-train}: Training Phase}, toprule=.15mm, colframe=quarto-callout-note-color-frame, toptitle=1mm, opacitybacktitle=0.6, left=2mm, titlerule=0mm, rightrule=.15mm, colbacktitle=quarto-callout-note-color!10!white]

@@

\begin{tcolorbox}[enhanced jigsaw, opacityback=0, bottomtitle=1mm, arc=.35mm, colback=white, coltitle=black, bottomrule=.15mm, breakable, leftrule=.75mm, title={Note \ref*{nte-tune_lr-eval}: Evaluation Phase}, toprule=.15mm, colframe=quarto-callout-note-color-frame, toptitle=1mm, opacitybacktitle=0.6, left=2mm, titlerule=0mm, rightrule=.15mm, colbacktitle=quarto-callout-note-color!10!white]

>>>>

\begin{tcolorbox}[enhanced jigsaw, left=2mm, toprule=.15mm, colbacktitle=quarto-callout-note-color!10!white, arc=.35mm, opacitybacktitle=0.6, colframe=quarto-callout-note-color-frame, breakable, bottomrule=.15mm, titlerule=0mm, title={Note \ref*{nte-train-default}: Training Phase}, colback=white, opacityback=0, bottomtitle=1mm, coltitle=black, toptitle=1mm, leftrule=.75mm, rightrule=.15mm]

@@

\begin{tcolorbox}[enhanced jigsaw, left=2mm, toprule=.15mm, colbacktitle=quarto-callout-note-color!10!white, arc=.35mm, opacitybacktitle=0.6, colframe=quarto-callout-note-color-frame, breakable, bottomrule=.15mm, titlerule=0mm, title={Note \ref*{nte-eval-default}: Evaluation Phase}, colback=white, opacityback=0, bottomtitle=1mm, coltitle=black, toptitle=1mm, leftrule=.75mm, rightrule=.15mm]

@@

\subsubsection{Integrated Gradients}\label{integrated-gradients}

\caption{\label{tbl-ig}Integrated gradients.}

\begin{tabular}{
l
S[table-format=2.2(3.2)]
S[table-format=2.2(2.2)]
}
  \toprule
  \textbf{Data} & \textbf{CT} & \textbf{BL} \\\midrule
  LS & 0.03 \pm 0.02 & 275.23 \pm 2389.26 \\
  Circ & 9.58 \pm 32.17 & 34.76 \pm 154.26 \\
  Moon & 15.05 \pm 44.79 & 0.69 \pm 0.5 \\
  OL & 1.38 \pm 2.24 & 7.9 \pm 12.03 \\\midrule
  Adult & 0.43 \pm 0.04 & 0.97 \pm 0.05 \\
  CH & 0.09 \pm 0.03 & 0.22 \pm 0.06 \\
  Cred & 0.0 \pm 0.01 & 0.43 \pm 0.06 \\
  GMSC & 1.0 \pm 0.0 & 0.26 \pm 0.13 \\
  MNIST & 0.18 \pm 0.02 & 0.43 \pm 0.06 \\
\end{tabular}

@@

\begin{tabular}{
l
S[table-format=2.2(1.2)]
}
  \toprule
  \textbf{Data} & \textbf{Cost $(-\%)$} \\\midrule
  LS & -26.82\pm0.86 $^{*}$ \\
  Circ & 40.97\pm0.82 $^{*}$ \\
  Moon & 33.83\pm0.98 $^{*}$ \\
  OL & 10.35\pm1.28 $^{*}$ \\\midrule
  Adult & 1.16\pm3.53 $^{}$ \\
  CH & -34.89\pm2.31 $^{*}$ \\
  Cred & 28.24\pm1.08 $^{*}$ \\
  GMSC & 3.54\pm5.78 $^{}$ \\
  MNIST & -31.67\pm7.72 $^{*}$ \\\midrule
  Avg. & 2.75 \\\bottomrule
\end{tabular}

@@

\begin{tcolorbox}[enhanced jigsaw, left=2mm, toprule=.15mm, colbacktitle=quarto-callout-note-color!10!white, arc=.35mm, opacitybacktitle=0.6, colframe=quarto-callout-note-color-frame, breakable, bottomrule=.15mm, titlerule=0mm, title={Note \ref*{nte-gen-params-final-run-train}: Training Phase}, colback=white, opacityback=0, bottomtitle=1mm, coltitle=black, toptitle=1mm, leftrule=.75mm, rightrule=.15mm]

@@

\begin{tcolorbox}[enhanced jigsaw, left=2mm, toprule=.15mm, colbacktitle=quarto-callout-note-color!10!white, arc=.35mm, opacitybacktitle=0.6, colframe=quarto-callout-note-color-frame, breakable, bottomrule=.15mm, titlerule=0mm, title={Note \ref*{nte-gen-params-final-run-eval}: Evaluation Phase}, colback=white, opacityback=0, bottomtitle=1mm, coltitle=black, toptitle=1mm, leftrule=.75mm, rightrule=.15mm]

@@

\begin{tcolorbox}[enhanced jigsaw, left=2mm, toprule=.15mm, colbacktitle=quarto-callout-note-color!10!white, arc=.35mm, opacitybacktitle=0.6, colframe=quarto-callout-note-color-frame, breakable, bottomrule=.15mm, titlerule=0mm, title={Note \ref*{nte-pen-final-run-train}: Training Phase}, colback=white, opacityback=0, bottomtitle=1mm, coltitle=black, toptitle=1mm, leftrule=.75mm, rightrule=.15mm]

@@

\begin{tcolorbox}[enhanced jigsaw, left=2mm, toprule=.15mm, colbacktitle=quarto-callout-note-color!10!white, arc=.35mm, opacitybacktitle=0.6, colframe=quarto-callout-note-color-frame, breakable, bottomrule=.15mm, titlerule=0mm, title={Note \ref*{nte-pen-final-run-eval}: Evaluation Phase}, colback=white, opacityback=0, bottomtitle=1mm, coltitle=black, toptitle=1mm, leftrule=.75mm, rightrule=.15mm]

@@

\begin{tcolorbox}[enhanced jigsaw, left=2mm, toprule=.15mm, colbacktitle=quarto-callout-note-color!10!white, arc=.35mm, opacitybacktitle=0.6, colframe=quarto-callout-note-color-frame, breakable, bottomrule=.15mm, titlerule=0mm, title={Note \ref*{nte-train-final-run-train}: Training Phase}, colback=white, opacityback=0, bottomtitle=1mm, coltitle=black, toptitle=1mm, leftrule=.75mm, rightrule=.15mm]

@@

\begin{tcolorbox}[enhanced jigsaw, left=2mm, toprule=.15mm, colbacktitle=quarto-callout-note-color!10!white, arc=.35mm, opacitybacktitle=0.6, colframe=quarto-callout-note-color-frame, breakable, bottomrule=.15mm, titlerule=0mm, title={Note \ref*{nte-train-final-run-eval}: Evaluation Phase}, colback=white, opacityback=0, bottomtitle=1mm, coltitle=black, toptitle=1mm, leftrule=.75mm, rightrule=.15mm]

@@

\begin{tcolorbox}[enhanced jigsaw, left=2mm, toprule=.15mm, colbacktitle=quarto-callout-note-color!10!white, arc=.35mm, opacitybacktitle=0.6, colframe=quarto-callout-note-color-frame, breakable, bottomrule=.15mm, titlerule=0mm, title={Note \ref*{nte-tune-train}: Training Phase}, colback=white, opacityback=0, bottomtitle=1mm, coltitle=black, toptitle=1mm, leftrule=.75mm, rightrule=.15mm]

@@

\begin{tcolorbox}[enhanced jigsaw, left=2mm, toprule=.15mm, colbacktitle=quarto-callout-note-color!10!white, arc=.35mm, opacitybacktitle=0.6, colframe=quarto-callout-note-color-frame, breakable, bottomrule=.15mm, titlerule=0mm, title={Note \ref*{nte-tune-eval}: Evaluation Phase}, colback=white, opacityback=0, bottomtitle=1mm, coltitle=black, toptitle=1mm, leftrule=.75mm, rightrule=.15mm]

@@

\begin{tcolorbox}[enhanced jigsaw, left=2mm, toprule=.15mm, colbacktitle=quarto-callout-note-color!10!white, arc=.35mm, opacitybacktitle=0.6, colframe=quarto-callout-note-color-frame, breakable, bottomrule=.15mm, titlerule=0mm, title={Note \ref*{nte-tune_lr-train}: Training Phase}, colback=white, opacityback=0, bottomtitle=1mm, coltitle=black, toptitle=1mm, leftrule=.75mm, rightrule=.15mm]

@@

\begin{tcolorbox}[enhanced jigsaw, left=2mm, toprule=.15mm, colbacktitle=quarto-callout-note-color!10!white, arc=.35mm, opacitybacktitle=0.6, colframe=quarto-callout-note-color-frame, breakable, bottomrule=.15mm, titlerule=0mm, title={Note \ref*{nte-tune_lr-eval}: Evaluation Phase}, colback=white, opacityback=0, bottomtitle=1mm, coltitle=black, toptitle=1mm, leftrule=.75mm, rightrule=.15mm]

### 2025-07-23 paper/sections/other/main_results.qmd
going with Alek's suggestions for standardization and baselines

@@

df = Serialization.deserialize("paper/experiments/output/costs.jls")
inputs = get_table_inputs(df, nothing; backend=Val(:latex))
tabulate_results(
    inputs; 
    table_type=:tabular,
    alignment = [:l, fill(:c, ncol(df)-1)...],
    wrap_table = false,
)

>>>>

### Integrated Gradients

:::{#tbl-ig}

df = Serialization.deserialize(joinpath(mtbl_dir, "ig.jls")) |>
    df -> transform(df, [:mean, :se] => ByRow((m, s) -> LatexCell("$(round(m, digits=2)) \\pm $(round(s, digits=2))")) => :mean) |>
    df -> select(df, Not(:se)) |>
    df -> DataFrames.unstack(df, :objective, :mean) |>
    df -> rename(df, :full => :CT, :vanilla => :BL) |>
    df -> transform(df, :data => ByRow(d  -> CTExperiments.format_header(d)) => :data)
inputs = get_table_inputs(df, nothing; backend=Val(:latex))
al = [
    "l", 
    "S[table-format=2.2(3.2)]", 
    "S[table-format=2.2(2.2)]"
] 
tabulate_results(
    inputs,
    al
    ; 
    table_type=:tabular,
    alignment = [:l, fill(:c, ncol(df)-1)...],
    wrap_table = false,
)

Integrated gradients.

@@

df = Serialization.deserialize("paper/experiments/output/costs.jls")
inputs = get_table_inputs(df, nothing; backend=Val(:latex))
al = [
    "l", 
    "S[table-format=2.2(1.2)]", 
]
tabulate_results(
    inputs, al; 
    table_type=:tabular,
    alignment = [:l, fill(:c, ncol(df)-1)...],
    wrap_table = false,
)
